---
title: "LabExercise#1_Gallenero"
output:
  html_document:
    df_print: paged
  pdf_document: default
date: "2024-02-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("dplyr")
install.packages("rvest")
install.packages("httr")
install.packages("polite")
install.packages("kableExtra")

library(dplyr)
library(rvest)
library(httr)
library(polite)
library(kableExtra)
polite::use_manners(save_as = 'polite_scrape.R')
```

FIRST CATEGORY: MAKEUP
```{r}
library(rvest)
library(polite)
library(httr)


Makeup_products <- data.frame()


MakeupLink1 <- "https://www.amazon.com.au/s?k=makeup&rh=n%3A5150071051&ref=nb_sb_noss"

session <- html_session(MakeupLink1,
                        user_agent = "For Educational Purpose")

scrapeNodes <- function(session, selector) {
  session %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

scrapedCategory <- "Makeup"

name1 <- scrapeNodes(session, "span.a-size-base-plus.a-color-base.a-text-normal")
name1 <- name1[1:35]

price1 <- scrapeNodes(session, "span.a-offscreen")
price1<- price1[1:35]

ratings1 <- scrapeNodes(session, "span.a-icon-alt")
ratings1 <- ratings1[1:35]

reviews1 <- scrapeNodes(session, "span.a-size-base.s-underline-text")
reviews1 <- reviews1[1:35]

Makeup_products <- data.frame(category = scrapedCategory,
                               name = name1,
                               price = price1,
                               ratings = ratings1,
                               no_of_reviews = reviews1)


###
      MakeupLink2 <- "https://www.amazon.com.au/s?k=makeup&i=beauty&rh=n%3A5150071051&page=2&qid=1707484287&ref=sr_pg_2"

    session2 <- html_session(MakeupLink2, user_agent = "For Educational Purpose")

      scrapeNodes <- function(session, selector) {
  session %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

scrapedCategory2 <- "Makeup"

name2 <- scrapeNodes(session2, "span.a-size-base-plus.a-color-base.a-text-normal")
name2 <- name2[1:35]

price2 <- scrapeNodes(session2, "span.a-offscreen")
price2 <- price2[1:35]

ratings2 <- scrapeNodes(session2, "span.a-icon-alt")
ratings2 <- ratings2[1:35]

reviews2 <- scrapeNodes(session2, "span.a-size-base.s-underline-text")
reviews2 <- reviews2[1:35]

Makeup_products <- data.frame(category = scrapedCategory2,
                               name = name2,
                               price = price2,
                               ratings = ratings2,
                               no_of_reviews = reviews2)




###
  
MakeupLink3 <- "https://www.amazon.com.au/s?k=makeup&i=beauty&rh=n%3A5150071051&page=3&qid=1707484298&ref=sr_pg_3"

session3 <- html_session(MakeupLink3, user_agent = "For Educational Purpose")

scrapedCategory3 <- "Makeup"

name3 <- scrapeNodes(session3, "span.a-size-base-plus.a-color-base.a-text-normal")
name3 <- name3[1:35]

price3 <- scrapeNodes(session3, "span.a-offscreen")
price3 <- price3[1:35]

ratings3 <- scrapeNodes(session3, "span.a-icon-alt")
ratings3 <- ratings3[1:35]

reviews3 <- scrapeNodes(session3, "span.a-size-base.s-underline-text")
reviews3 <- reviews3[1:35]

Makeup_products <- rbind(Makeup_products, data.frame(category = scrapedCategory3,
                                                       name = name3,
                                                       price = price3,
                                                       ratings = ratings3,
                                                       no_of_reviews = reviews3))



###

MakeupLink4 <- "https://www.amazon.com.au/s?k=makeup&i=beauty&rh=n%3A5150071051&page=4&qid=1707464624&ref=sr_pg_4"

session4 <- html_session(MakeupLink4, user_agent = "For Educational Purpose")

scrapedCategory4 <- "Makeup"

name4 <- scrapeNodes(session4, "span.a-size-base-plus.a-color-base.a-text-normal")
name4 <- name4[1:35]

price4 <- scrapeNodes(session4, "span.a-offscreen")
price4 <- price4[1:35]

ratings4 <- scrapeNodes(session4, "span.a-icon-alt")
ratings4 <- ratings4[1:35]

reviews4 <- scrapeNodes(session4, "span.a-size-base.s-underline-text")
reviews4 <- reviews4[1:35]

Makeup_products <- rbind(Makeup_products, data.frame(category = scrapedCategory4,
                                                       name = name4,
                                                       price = price4,
                                                       ratings = ratings4,
                                                       no_of_reviews = reviews4))

Makeup_products <- Makeup_products[1:100,]


Makeup_products


```

SECOND CATEGORY: LUGGAGE
```{r}

library(rvest)
library(polite)
library(httr)


luggage_products <- data.frame()


luggagelink1 <- "https://www.amazon.com.au/s?k=luggage&crid=35Y2D9DG1HBJA&sprefix=luggag%2Caps%2C373&ref=nb_sb_noss_2"

session <- html_session(luggagelink1,
                        user_agent = "For Educational Purpose")

scrapeNodes <- function(session, selector) {
  session %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

scrapedCategory <- "Luggage"

name1 <- scrapeNodes(session, "span.a-size-base-plus.a-color-base.a-text-normal")
name1 <- name1[1:40]

price1 <- scrapeNodes(session, "span.a-offscreen")
price1 <- price1[1:40]

ratings1 <- scrapeNodes(session, "span.a-icon-alt")
ratings1 <- ratings1[1:40]

reviews1 <- scrapeNodes(session, "span.a-size-base.s-underline-text")
reviews1 <- reviews1[1:40]

luggage_products <- data.frame(category = scrapedCategory,
                               name = name1,
                               price = price1,
                               ratings = ratings1,
                               no_of_reviews = reviews1)


###
      luggagelink2 <- "https://www.amazon.com.au/s?k=luggage&page=2&crid=35Y2D9DG1HBJA&qid=1707455578&sprefix=luggag%2Caps%2C373&ref=sr_pg_2"

    session2 <- html_session(luggagelink2, user_agent = "For Educational Purpose")

      scrapeNodes <- function(session, selector) {
  session %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

scrapedCategory2 <- "Luggage"

name2 <- scrapeNodes(session2, "span.a-size-base-plus.a-color-base.a-text-normal")
name2 <- name2[1:40]

price2 <- scrapeNodes(session2, "span.a-offscreen")
price2 <- price2[1:40]

ratings2 <- scrapeNodes(session2, "span.a-icon-alt")
ratings2 <- ratings2[1:40]

reviews2 <- scrapeNodes(session2, "span.a-size-base.s-underline-text")
reviews2 <- reviews2[1:40]

luggage_products <- rbind(luggage_products, data.frame(category = scrapedCategory2,
                                                       name = name2,
                                                       price = price2,
                                                       ratings = ratings2,
                                                       no_of_reviews = reviews2))




###
  
luggagelink3 <- "https://www.amazon.com.au/s?k=luggage&page=3&crid=35Y2D9DG1HBJA&qid=1707456756&sprefix=luggag%2Caps%2C373&ref=sr_pg_3"

session3 <- html_session(luggagelink3, user_agent = "For Educational Purpose")

scrapedCategory3 <- "Luggage"

name3 <- scrapeNodes(session3, "span.a-size-base-plus.a-color-base.a-text-normal")
name3 <- name3[1:48]

price3 <- scrapeNodes(session3, "span.a-offscreen")
price3 <- price3[1:48]

ratings3 <- scrapeNodes(session3, "span.a-icon-alt")
ratings3 <- ratings3[1:48]

reviews3 <- scrapeNodes(session3, "span.a-size-base.s-underline-text")
reviews3 <- reviews3[1:48]

luggage_products <- rbind(luggage_products, data.frame(category = scrapedCategory3,
                                                       name = name3,
                                                       price = price3,
                                                       ratings = ratings3,
                                                       no_of_reviews = reviews3))




###

luggagelink4 <- "https://www.amazon.com.au/s?k=luggage&page=4&crid=35Y2D9DG1HBJA&qid=1707456887&sprefix=luggag%2Caps%2C373&ref=sr_pg_4"

session4 <- html_session(luggagelink4, user_agent = "For Educational Purpose")

scrapedCategory4 <- "Luggage"

name4 <- scrapeNodes(session4, "span.a-size-base-plus.a-color-base.a-text-normal")
name4 <- name4[1:40]

price4 <- scrapeNodes(session4, "span.a-offscreen")
price4 <- price4[1:40]

ratings4 <- scrapeNodes(session4, "span.a-icon-alt")
ratings4 <- ratings4[1:40]

reviews4 <- scrapeNodes(session4, "span.a-size-base.s-underline-text")
reviews4 <- reviews4[1:40]

luggage_products <- rbind(luggage_products, data.frame(category = scrapedCategory4,
                                                       name = name4,
                                                       price = price4,
                                                       ratings = ratings4,
                                                       no_of_reviews = reviews4))

luggage_products <- luggage_products[1:100,]


luggage_products

```

```{r}
scraped_products <- rbind(luggage_products, Makeup_products)
scraped_products
```
```

THE TEN PRODUCTS
PRODUCT #1

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product1 = data.frame()
scrapedCategory <- "Makeup"


  link = "https://www.amazon.com.au/colors-Professional-Makeup-Women-Full/product-reviews/B09QRTWQRC/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product1 <- rbind(product1, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
                         

      link2 = "https://www.amazon.com.au/colors-Professional-Makeup-Women-Full/product-reviews/B09QRTWQRC/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product1 <- rbind(product1, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
  

      link3 = "https://www.amazon.com.au/colors-Professional-Makeup-Women-Full/product-reviews/B09QRTWQRC/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product1 <- rbind(product1, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product1)
```

PRODUCT #2
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product2 = data.frame()
scrapedCategory <- "Makeup"


#LINK 1

  link = "https://www.amazon.com.au/LOreal-Paris-Match-Concealer-Vanilla/product-reviews/B073QT9968/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product2 <- rbind(product2, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
#LINK 2

      link2 = "https://www.amazon.com.au/LOreal-Paris-Match-Concealer-Vanilla/product-reviews/B073QT9968/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product2 <- rbind(product2, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
#LINK 3
      
      link3 = "https://www.amazon.com.au/LOreal-Paris-Match-Concealer-Vanilla/product-reviews/B073QT9968/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product2 <- rbind(product2, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product2)
```

PRODUCT #3
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product3 = data.frame()
scrapedCategory <- "Makeup"


#LINK 1

  link = "https://www.amazon.com.au/Maybelline-Lasting-Makeup-Setting-Spray/product-reviews/B07QV2MD3D/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product3 <- rbind(product3, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
#LINK 2

      link2 = "https://www.amazon.com.au/Maybelline-Lasting-Makeup-Setting-Spray/product-reviews/B07QV2MD3D/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product3 <- rbind(product3, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
#LINK 3
      
      link3 = "https://www.amazon.com.au/Maybelline-Lasting-Makeup-Setting-Spray/product-reviews/B07QV2MD3D/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product3 <- rbind(product3, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product3)
```

PRODUCT#4
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product4 = data.frame()
scrapedCategory <- "Makeup"


#LINK 1

  link = "https://www.amazon.com.au/1000-HOUR-Eyelash-Brown-Black/product-reviews/B00FAANCUK/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product4 <- rbind(product4, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
#LINK 2

      link2 = "https://amazon.com.au/1000-HOUR-Eyelash-Brown-Black/product-reviews/B00FAANCUK/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product4 <- rbind(product4, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
#LINK 3
      
      link3 = "https://www.amazon.com.au/1000-HOUR-Eyelash-Brown-Black/product-reviews/B00FAANCUK/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product4 <- rbind(product4, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product4)
```

PRODUCT#5
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product5 = data.frame()
scrapedCategory <- "Makeup"


#LINK 1

  link = "https://www.amazon.com.au/0ml-Warm-Neutrals-PROFESSIONAL-Ultimate/product-reviews/B01IW02HX2/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product5 <- rbind(product5, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
#LINK 2

      link2 = "https://www.amazon.com.au/0ml-Warm-Neutrals-PROFESSIONAL-Ultimate/product-reviews/B01IW02HX2/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product5 <- rbind(product5, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
#LINK 3
      
      link3 = "https://www.amazon.com.au/0ml-Warm-Neutrals-PROFESSIONAL-Ultimate/product-reviews/B01IW02HX2/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product5 <- rbind(product5, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product5)
```

PRODUCT #6
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product6 = data.frame()
scrapedCategory <- "Luggage"


#LINK 1

  link = "https://www.amazon.com.au/SHOWKOO-Luggage-Expandable-Suitcase-set-Orange/product-reviews/B09NXQ2F4R/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product6 <- rbind(product6, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
#LINK 2

      link2 = "https://www.amazon.com.au/0ml-Warm-Neutrals-PROFESSIONAL-Ultimate/product-reviews/B01IW02HX2/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product6 <- rbind(product6, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
#LINK 3
      
      link3 = "https://www.amazon.com.au/0ml-Warm-Neutrals-PROFESSIONAL-Ultimate/product-reviews/B01IW02HX2/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product6 <- rbind(product6, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product6)
```

PRODUCT #7
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product7 = data.frame()
scrapedCategory <- "Luggage"


# LINK 1

  link = "https://www.amazon.com.au/Amazon-Basics-Hardside-Hard-Shell-Suitcase/product-reviews/B071VG5N9D/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product7 <- rbind(product7, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
# LINK 2

      link2 = "https://www.amazon.com.au/Amazon-Basics-Hardside-Hard-Shell-Suitcase/product-reviews/B071VG5N9D/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product7 <- rbind(product7, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
# LINK 3
      
      link3 = "https://www.amazon.com.au/Amazon-Basics-Hardside-Hard-Shell-Suitcase/product-reviews/B071VG5N9D/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product7 <- rbind(product7, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product7)

```

PRODUCT #8
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product8 = data.frame()
scrapedCategory <- "Luggage"


# LINK 1

  link = "https://www.amazon.com.au/Rockland-Melbourne-Expandable-Carry-Charcoal/product-reviews/B015DC201G/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product8 <- rbind(product8, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
## LINK2

      link2 = "https://www.amazon.com.au/Rockland-Melbourne-Expandable-Carry-Charcoal/product-reviews/B015DC201G/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product8 <- rbind(product8, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
#LINK 3     
      
      link3 = "https://www.amazon.com.au/Rockland-Melbourne-Expandable-Carry-Charcoal/product-reviews/B015DC201G/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product8 <- rbind(product8, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product8)
```

PRODUCT #9
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product9 = data.frame()
scrapedCategory <- "Luggage"


#

  link = "https://www.amazon.com.au/Samsonite-Oc2lite-Suitcase/product-reviews/B0CR3WKRJ1/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product9 <- rbind(product9, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
#

      link2 = "https://www.amazon.com.au/Samsonite-Oc2lite-Suitcase/product-reviews/B0CR3WKRJ1/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product9 <- rbind(product9, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
      
#
      
      link3 = "https://www.amazon.com.au/Samsonite-Oc2lite-Suitcase/product-reviews/B0CR3WKRJ1/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product9 <- rbind(product9, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product9)
```

PRODUCT #10
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product10 = data.frame()
scrapedCategory <- "Luggage"


 #LINK1

  link = "https://www.amazon.com.au/American-Tourister-Airconic-Opening-Suitcase/product-reviews/B0CR3RZ1SX/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
  
      sessionProd1 <- bow(link,
               user_agent = "For Educational Purpose")
  
      scrapeNodes <- function(selector){
      scrape(sessionProd1) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
      }
          
      scrapedprodName <- scrapeNodes("h1.a-size-large.a-text-ellipsis")
    
      
      prodReviewer1 <- scrapeNodes("span.a-profile-name")
      prodReviewer1 <- prodReviewer1[1:10]

      
      prodReview1 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview1 <- prodReview1[1:10]

      
      prodDate1 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate1 <- prodDate1[1:10]

      
      prodRating1 <- scrapeNodes("span.a-icon-alt")
      prodRating1 <- prodRating1[1:10]

      
      product10 <- rbind(product10, data.frame(category = scrapedCategory,name = scrapedprodName,
                          reviewer = prodReviewer1,
                          review = prodReview1,
                          date = prodDate1,
                         ratings = prodRating1))
 #LINK2

      link2 = "https://www.amazon.com.au/American-Tourister-Airconic-Opening-Suitcase/product-reviews/B0CR3RZ1SX/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
  
  sessionProd2 <- bow(link2,
               user_agent = "For Educational Purpose")


      prodReviewer2 <- scrapeNodes("span.a-profile-name")
      prodReviewer2 <- prodReviewer2[1:10]

      
      prodReview2 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview2 <- prodReview2[1:10]

      
      prodDate2 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate2 <- prodDate2[1:10]

      
      prodRating2 <- scrapeNodes("span.a-icon-alt")
      prodRating2 <- prodRating2[1:10]

      
      product10 <- rbind(product10, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer2,
                          review = prodReview2,
                          date = prodDate2,
                         ratings = prodRating2))
      
#
      
      link3 = "https://www.amazon.com.au/American-Tourister-Airconic-Opening-Suitcase/product-reviews/B0CR3RZ1SX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
  
  sessionProd3 <- bow(link3,
               user_agent = "For Educational Purpose")


      
      prodReviewer3 <- scrapeNodes("span.a-profile-name")
      prodReviewer3 <- prodReviewer3[1:10]

      
      prodReview3 <- scrapeNodes("span.a-size-base.review-text.review-text-content")
      prodReview3 <- prodReview3[1:10]

      
      prodDate3 <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")
      prodDate3 <- prodDate3[1:10]

      
      prodRating3 <- scrapeNodes("span.a-icon-alt")
      prodRating3 <- prodRating3[1:10]

      
      product10 <- rbind(product10, data.frame(category = scrapedCategory ,name = scrapedprodName,
                          reviewer = prodReviewer3,
                          review = prodReview3,
                          date = prodDate3,
                         ratings = prodRating3))
      
print(product10)
```


```{r}
All_Reviews <- rbind(product1, product2, product3, product4, product5, product6, product7, product8, product9, product10)

print(All_Reviews)
```