---
title: "Pract_Exam_Gallenero"
output:
  html_document: default
  pdf_document: default
date: "2024-03-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#A Load the built-warpbreaks dataset
```{r}
#Load the warpbreaks dataset
data ("warpbreaks")
```

#1. Find out, in a single command, which columns of warpbreaks are either numeric or integer.
```{r}
Numeric_cols <- sapply(warpbreaks, is.numeric)
Numeric_cols


#2. Is numeric a natural data type for the columns which are stored as such? Convert tointeger when necessary.
Integer_cols <- sapply(warpbreaks, is.integer)
Integer_cols


numeric_or_integer_cols <- warpbreaks[, Numeric_cols| Integer_cols]
numeric_or_integer_cols
```


#Error messages in R sometimes report the underlying type of an object rather than theuser-level class. Derive from the following code and error message what theunderlying type.

for (i in 1:ncol(numeric_or_integer_columns)) {
  if (!is.integer(numeric_or_integer_columns[, i])) {
    numeric_or_integer_columns[, i] <- as.integer(numeric_or_integer_columns[, i])
  }
}
```{r}
#4 ERROR MESSAGE
#Error in 1:ncol(numeric_or_integer_columns) : argument of length 0
```


#B. Load the example.File.txt
#B
```{r}
#Read the complete file using readLines.
lines <- readLines("exampleFile.txt")

#Separate the vector of lines into a vector containing comments and a vector containing the data. Hint: use grepl.
comments <- lines[grepl("^//", lines)]
comments

data_lines <- lines[!grepl("^//", lines)]
data_lines

#Extract the date from the first comment line.

date <- gsub("^// Survey data. Created : ", "", comments[1])
date
```
#a. Split the character vectors in the vector containing data lines by semicolon (;) using strsplit.
```{r}
split_data <- strsplit(data_lines, ";")
split_data
```
#Find the maximum number of fields retrieved by split. Append rows that are shorter with NA's.
```{r}

max_fields <- max(sapply(split_data, length))
max_fields

split_data <- lapply(split_data, function(x) c(x, rep(NA, max_fields - length(x))))
split_data
```
#Use unlist and matrix to transform the data to row-column format.
```{r}
data_matrix <- matrix(unlist(split_data), ncol = max_fields, byrow = TRUE)
data_matrix
```
#From comment lines 2-4, extract the names of the fields. Set these as colnames for the matrix you just created.
```{r}
fieldNames <- gsub("^// Field [0-9]+: ", "", comments[2:4])
fieldNames

colnames(data_matrix) <- fieldNames
colnames(data_matrix)
```
