---
title: "Lab_Exercise#2_Gallenero"
date: "2024-02-21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

Amazon_Reviews_Scrape <- function(product_name, url_stub, pages) {
  prod_df <- data.frame()

  for (page in pages) {
    link <- paste0("https://www.amazon.com.au/",url_stub,"/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
    session <- bow(link, user_agent = "Educational Purpose")
    
    scrapeNodes <- function(selector) {
      scrape(session) %>%
        html_nodes(selector) %>%
        html_text(trim = TRUE)
    }

    scrape_Title <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
    scrape_Reviewer <- scrapeNodes("span.a-profile-name")[1:10]
    scrape_Review <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
    scrape_Date <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
    scrape_Rating <- scrapeNodes("span.a-icon-alt")[1:10]
    scrape_Type <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

    prod_df <- rbind(prod_df, data.frame(
      prod_name = product_name,
      title = scrape_Title,
      reviewer = scrape_Reviewer,
      review = scrape_Review,
      date = scrape_Date,
      ratings = scrape_Rating,
      type_of_purchase = scrape_Type
    ))

    Sys.sleep(3)
  }

  return(prod_df)
}
```


CATEGORY: MAKEUP
PRODUCT 1

```{r}
    
product1 <- Amazon_Reviews_Scrape(
  "Maybelline-Instant-Rewind-Circles-Concealer",
  "Maybelline-Instant-Rewind-Circles-Concealer/product-reviews/B004Y9GTYE",
  6:10
)
```
PRODUCT 2
```{r}
product2 <- Amazon_Reviews_Scrape(
  "Real-Technique-Miracle-Complexion-Sponge",
  "Real-Technique-Miracle-Complexion-Sponge/product-reviews/B01JINOV5E",
  6:10
)
```
PRODUCT 3

```{r}
product3 <- Amazon_Reviews_Scrape(
  "Pieces-Powder-Makeup-Velour-Triangle",
  "Pieces-Powder-Makeup-Velour-Triangle/product-reviews/B09V5RDKP4",
  6:10
)
```

PRODUCT 4
```{r}
product4 <- Amazon_Reviews_Scrape(
  "SHEGLAM-Liquid-Makeup-Cheeks-Finish",
  "SHEGLAM-Liquid-Makeup-Cheeks-Finish/product-reviews/B0BHFBBH25",
  6:10
)
```
PRODUCT 5
```{r}
product5 <- Amazon_Reviews_Scrape(
  "l-f-Monochromatic-Multi-Cheeks-Dazzling",
  "l-f-Monochromatic-Multi-Cheeks-Dazzling/product-reviews/B088W7L534",
  6:10
)
```
PRODUCT 6
```{r}
product6 <- Amazon_Reviews_Scrape(
  "Paris-Makeup-True-Natural-Glow-Illuminator-Highlighter-Day-Radiant-Glow",
  "Paris-Makeup-True-Natural-Glow-Illuminator-Highlighter-Day-Radiant-Glow/product-reviews/B074PTZCNX",
  6:10
)
```
PRODUCT 7
```{r}
product7 <- Amazon_Reviews_Scrape(
  "Maybelline-Volumizing-Buildable-Lengthening-Multiplying",
  "Maybelline-Volumizing-Buildable-Lengthening-Multiplying/product-reviews/B08H3JPH74",
  6:10
)
```
PRODUCT 8
```{r}
product8 <- Amazon_Reviews_Scrape(
  "NYX-Professional-Makeup-Shine-Colour",
  "NYX-Professional-Makeup-Shine-Colour/product-reviews/B08TJR1YS6",
  6:10
)
```

PRODUCT 9
```{r}
product9 <- Amazon_Reviews_Scrape(
  "l-f-Poreless-Primer-Fluid-Ounce",
  "l-f-Poreless-Primer-Fluid-Ounce/product-reviews/B00JZ4V6V4",
  6:10
)
```

PRODUCT 10
```{r}
product10 <- Amazon_Reviews_Scrape(
  "Maybelline-SuperStay-Matte-Spiced-Caller",
  "Maybelline-SuperStay-Matte-Spiced-Caller/product-reviews/B08H3QV41W",
  6:10
)
```

PRODUCT 11
```{r}
product11 <- Amazon_Reviews_Scrape(
  "All-One-Makeup-Gift-Kit",
  "All-One-Makeup-Gift-Kit/product-reviews/B081YZ4CFZ",
  6:10
)
```

PRODUCT 12
```{r}
product12 <- Amazon_Reviews_Scrape(
  "Maybelline-SuperStay-Matte-Spiced-Caller",
  "Maybelline-SuperStay-Matte-Spiced-Caller/product-reviews/B08H3QV41W",
  6:10
)
```

PRODUCT 13
```{r}
product13 <- Amazon_Reviews_Scrape(
  "LOreal-Paris-Infallible-Automatic-Intense",
  "LOreal-Paris-Infallible-Automatic-Intense/product-reviews/B09NQGDDGF",
  6:10
)
```

PRODUCT 14
```{r}
product14 <- Amazon_Reviews_Scrape(
  "Revolution-Loose-Baking-Powder-Banana",
  "Revolution-Loose-Baking-Powder-Banana/product-reviews/B081X3KTGW",
  6:10
)
```

PRODUCT 15
```{r}
product15 <- Amazon_Reviews_Scrape(
  "KIMUSE-Contour-1Contouring-Highlight",
  "KIMUSE-Contour-1Contouring-Highlight-W04-FAIR/product-reviews/B0BJ1VYD8Q",
  6:10
)
```

PRODUCT 16
```{r}
product16 <- Amazon_Reviews_Scrape(
  "Conceal-Correct-Contour-Palette-3CP01",
  "Conceal-Correct-Contour-Palette-3CP01/product-reviews/B00OU154OW",
  3:7
)
```

PRODUCT 17
```{r}
product17 <- Amazon_Reviews_Scrape(
  "Lipstick-FirstFly-Nutritious-Moisturizer-Temperature",
  "Lipstick-FirstFly-Nutritious-Moisturizer-Temperature/product-reviews/B078VR8SHC",
  6:10
)
```

PRODUCT 18
```{r}
product18 <- Amazon_Reviews_Scrape(
  "LOréal-Paris-Telescopic-Mascara-Black",
  "LOréal-Paris-Telescopic-Mascara-Black/product-reviews/B07QXG6ZPQ",
  6:10
)
```

PRODUCT 19
```{r}
product19 <- Amazon_Reviews_Scrape(
  "Lipstick-Plumper-Waterproof-Pigmented-Halloween",
  "Lipstick-Plumper-Waterproof-Pigmented-Halloween/product-reviews/B089FBPMC6",
  6:10
)
```

PRODUCT 20
```{r}
product20 <- Amazon_Reviews_Scrape(
  "KIMUSE-Makeup-Cheeks-Contour-Highlighter",
  "KIMUSE-Makeup-Cheeks-Contour-Highlighter/product-reviews/B09JSWZDX7",
  3:7
)
```

PRODUCT 21
```{r}
product21 <- Amazon_Reviews_Scrape(
  "Small-Makeup-Bag-Cosmetic-blue",
  "Small-Makeup-Bag-Cosmetic-blue/product-reviews/B0987RQ893",
  1:5
)
```

PRODUCT 22
```{r}
product22 <- Amazon_Reviews_Scrape(
  "Rimmel-London-Brow-Eyebrow-Sculpting",
  "Rimmel-London-Brow-Eyebrow-Sculpting/product-reviews/B00MGK9Q9S",
  1:5
)
```

PRODUCT 23
```{r}
product23 <- Amazon_Reviews_Scrape(
  "Maybelline-SuperStay-Matte-Spiced-Caller",
  "Maybelline-SuperStay-Matte-Spiced-Caller/product-reviews/B08H3QV41W",
  1:5
)
```

PRODUCT 24
```{r}
product24 <- Amazon_Reviews_Scrape(
  "Maybelline-SuperStay-Crayon-Lipstick-Adventure",
  "Maybelline-SuperStay-Crayon-Lipstick-Adventure/product-reviews/B07PDMYBYF",
  1:5
)
```

PRODUCT 25
```{r}
product25 <- Amazon_Reviews_Scrape(
  "NYX-Professional-Makeup-Brightening-Primer",
  "NYX-Professional-Makeup-Brightening-Primer/product-reviews/B08MRF16MK",
  2:6
)
```

PRODUCT 26
```{r}
product26 <- Amazon_Reviews_Scrape(
  "NEJLSD-Eyeliner-Eyeshadow-Blending-Foundation",
  "NEJLSD-Eyeliner-Eyeshadow-Blending-Foundation/product-reviews/B07FFMGYFY",
  3:7
)
```

PRODUCT 27
```{r}
product27 <- Amazon_Reviews_Scrape(
  "Daybreak-LOreal-Paris-Cosmetics-Boosting",
  "Daybreak-LOreal-Paris-Cosmetics-Boosting/product-reviews/B074PQ6XDN",
  3:7
)
```

PRODUCT 28
```{r}
product28 <- Amazon_Reviews_Scrape(
  "NYX-PROFESSIONAL-MAKEUP-Peekaboo-Neutral",
  "NYX-PROFESSIONAL-MAKEUP-Peekaboo-Neutral/product-reviews/B07B16HMSM",
  3:7
)
```

```{r}
product29 <- Amazon_Reviews_Scrape(
  "SFXULIX-Capacity-Travel-Cosmetic-Bag",
  "SFXULIX-Capacity-Travel-Cosmetic-Bag/product-reviews/B0BMWV2RK6",
  1:5
)
```

PRODUCT 30
```{r}
product30 <- Amazon_Reviews_Scrape(
  "Upgraded-Magnifying-Magnification-Application-Blackhead",
  "Upgraded-Magnifying-Magnification-Application-Blackhead/product-reviews/B0915FFTS7",
  1:5
)
```

PRODUCT 31
```{r}
product31 <- Amazon_Reviews_Scrape(
  "Laptop-Makeup-Make-Up-Palette",
  "Laptop-Makeup-Make-Up-Palette/product-reviews/B075Z4CHHD",
  3:7
)
```

PRODUCT 32
```{r}
product32 <- Amazon_Reviews_Scrape(
  "NYX-Professional-Makeup-Setting-Lasting",
  "NYX-Professional-Makeup-Setting-Lasting/product-reviews/B00B4YVU4G",
  2:6
)
```

PRODUCT 33
```{r}
product33 <- Amazon_Reviews_Scrape(
  "Cleaner-Super-Fast-Electric-Machine-Automatic",
  "Cleaner-Super-Fast-Electric-Machine-Automatic/product-reviews/B083LX58T8",
  3:7
)
```

PRODUCT 34
```{r}
product34 <- Amazon_Reviews_Scrape(
  "Cosmetic-Toiletry-Organizer-Portable-Adjustable",
  "Cosmetic-Toiletry-Organizer-Portable-Adjustable/product-reviews/B0785P1VP9",
  1:5
)
```

PRODUCT 35
```{r}
product35 <- Amazon_Reviews_Scrape(
  "Physicians-Formula-Murumuru-Bronzer-Sunkissed",
  "Physicians-Formula-Murumuru-Bronzer-Sunkissed/product-reviews/B077QCKV43",
  2:6
)
```

PRODUCT 36
```{r}
product36 <- Amazon_Reviews_Scrape(
  "FOCALLURE-Highlighter-Cruelty-Free-Illuminator-Highlighters",
  "FOCALLURE-Highlighter-Cruelty-Free-Illuminator-Highlighters/product-reviews/B096S7DZ78",
  3:7
)
```

PRODUCT 37
```{r}
product37 <- Amazon_Reviews_Scrape(
  "MAANGE-Foundation-Eyeshadow-Blending-Concealers",
  "MAANGE-Foundation-Eyeshadow-Blending-Concealers/product-reviews/B0C2C2S9LG",
  3:7
)
```

PRODUCT 38
```{r}
product38 <- Amazon_Reviews_Scrape(
  "NYX PROFESSIONAL-MAKEUP-Wonder-Universal",
  "NYX-PROFESSIONAL-MAKEUP-Wonder-Universal/product-reviews/B00TKJIF5O",
  1:5
)
```

PRODUCT 39
```{r}
product39 <- Amazon_Reviews_Scrape(
  "MAANGE-Professional-Foundation-Eyeshadow-Blackgold",
  "MAANGE-Professional-Foundation-Eyeshadow-Blackgold/product-reviews/B0991RTYH3",
  1:5
)
```

PRODUCT 40
```{r}
product40 <- Amazon_Reviews_Scrape(
  "Maybelline-SuperStay-Matte-Spiced-Caller",
  "Maybelline-SuperStay-Matte-Spiced-Caller/product-reviews/B08H3QV41W",
  3:7
)

```

PRODUCT 41
```{r}
product41 <- Amazon_Reviews_Scrape(
  "Maybelline-SuperStay-Crayon-Lipstick-Adventure",
  "Maybelline-SuperStay-Crayon-Lipstick-Adventure/product-reviews/B07PDMYBYF",
  2:6
)
```

PRODUCT 42
```{r}
product42 <- Amazon_Reviews_Scrape(
  "BS-MALL-Brushes-Synthetic-Foundation-Concealers",
  "BS-MALL-Brushes-Synthetic-Foundation-Concealers/product-reviews/B01LZ3RLPC",
  3:7
)
```

PRODUCT 43
```{r}
product43 <- Amazon_Reviews_Scrape(
  "Real-Technique-Expert-Concealer-Brush",
  "Real-Technique-Expert-Concealer-Brush/product-reviews/B01N0L42FZ",
  2:6
)
```

PRODUCT 44
```{r}
product44 <- Amazon_Reviews_Scrape(
  "Senbowe-Upgraded-Electric-Cosmetic-Automatic",
  "Senbowe-Upgraded-Electric-Cosmetic-Automatic/product-reviews/B0855DXKL8",
  3:7
)
```

PRODUCT 45
```{r}
product45 <- Amazon_Reviews_Scrape(
  "FERYES-Silicon-Portable-Cosmetic-Organizer",
  "FERYES-Silicon-Portable-Cosmetic-Organizer/product-reviews/B0B14V6F8T",
  3:7
)
```

PRODUCT 46
```{r}
product46 <- Amazon_Reviews_Scrape(
  "MAANGE-Professional-Foundation-Eyeshadow-Blackgold",
  "MAANGE-Professional-Foundation-Eyeshadow-Blackgold/product-reviews/B0991RTYH3",
  1:5
)
```

PRODUCT 47
```{r}
product47 <- Amazon_Reviews_Scrape(
  "Fancii-Magnifying-Flexible-Gooseneck-Daylight",
  "Fancii-Magnifying-Flexible-Gooseneck-Daylight/product-reviews/B07WHKZSK8",
  2:6
)
```

PRODUCT 48
```{r}
product48 <- Amazon_Reviews_Scrape(
  "Makeup-Cosmetic-Hand-Portable-Toiletry-Organizer",
  "Makeup-Cosmetic-Hand-Portable-Toiletry-Organizer/product-reviews/B0981V4R1B",
  3:7
)
```

PRODUCT 49
```{r}
product49 <- Amazon_Reviews_Scrape(
  "Jessup-Professional-Foundation-eyelashes-Natural-Synthetic",
  "Jessup-Professional-Foundation-eyelashes-Natural-Synthetic/product-reviews/B076DTSQQL",
  2:6
)
```

PRODUCT 50
```{r}
product50 <- Amazon_Reviews_Scrape(
  "Concealer-Foundation-Applicator-maquillaje-profesional",
  "Concealer-Foundation-Applicator-maquillaje-profesional/product-reviews/B0BWVXMWF5",
  3:7
)
```

ALL 50 PRODUCTS
```{r}

All50_Prod_Reviews = data.frame();

All50_Prod_Reviews  <- rbind(All50_Prod_Reviews, product1, product2, product3, product4, product5, product6, product7, product8, product9, product10,product11, product12, product13, product14, product15, product16, product16, product18, product19, product20, product21, product22, product23, product24, product25, product26, product27, product28, product29, product30, product31, product32, product33, product34, product35, product36, product37, product38, product39, product40, product41, product42, product43, product44, product45, product46, product47, product48, product49, product50)

#View(all_Products)
```

CSV
```{r}
write.csv(All50_Prod_Reviews, "All_50Product_Reviews")

```